\documentclass[a4paper,11pt]{article} 

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{multirow} 
\usepackage{booktabs} 
\usepackage{graphicx} 
\usepackage{setspace}
\usepackage[skip=6pt plus1pt, indent=0pt]{parskip}

\usepackage{float}
\usepackage{fancyhdr}

\usepackage{tcolorbox}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue
}

\usepackage[margin=1in]{geometry}

\newcommand{\incode}[1]{
\begin{tcolorbox}[colback=blue!5!white, boxrule=0mm, sharp corners]
\texttt{#1}
\end{tcolorbox}
}

\newcommand{\note}[1]{\textit{\textcolor{gray}{#1}}}

\pagestyle{fancy} 
\fancyhf{} 
\lhead{Advanced Computer Networks 2022}
\rhead{Lin Wang, George Karlos, Florian Gerlinghoff} 
\cfoot{\thepage} 

\begin{document}


\thispagestyle{empty} 

\begin{tabular}{@{}p{15.5cm}} 
{\bf Advanced Computer Networks 2022} \\
Vrije Universiteit Amsterdam  \\ Lin Wang, George Karlos, Florian Gerlinghoff\\
\hline 
\\
\end{tabular} 

\vspace*{0.3cm} 

{\Large \bf Lab5: Switches Do Dream Of Machine Learning! (Report)} 

\vspace*{0.3cm} 

%============== Please do not change anything above ==============%

% Please modify this part with your group information
\begin{tcolorbox}[sharp corners, colback=blue!5!white]
\begin{tabular}{@{}ll}
\textbf{Group number:} & <your group number on Canvas> \\
\textbf{Group members:} & <names of group members> \\
\textbf{Slip days used:} & <number of slip days used> \\
\textbf{Bonus claims:} & <what bonus?> \\
\end{tabular}
\end{tcolorbox}

\vspace{0.4cm}

\section{Basic In-Network Aggregation}

% Start your writing here, feel free to include subsections to structure your report if needed
% Please remove the note below in your submission
\note{Describe your aggregation protocol. What do workers do, what does the switch do, etc?}

\subsection{Ethernet Communication}

% Start your writing here. Please remove the note below in your submission
\note{Describe how your aggregation protocol works over Ethernet.}

\subsection{UDP Communication}

% Start your writing here. Please remove the note below in your submission
\note{Describe how your aggregation protocol works over UDP Sockets.}

\section{Basic Implementation}

% Start your writing here, feel free to include subsections to structure your report if needed
% Please remove the note below in your submission
\note{Describe how your solution is implemented on both host and (especially) switch side. Please include discussions for both Ethernet and UDP implementations. A good place to start is the questions and hints from the Lab 5 document.}

\subsection{How to Run It}

% Start your writing here. Please remove the note below in your submission
\note{If you made any changes on how the workers start, control plane usage, etc, please include them here; otherwise remove this section.}
 
\section{Fault-Tolerant Aggregation Protocol}

% Start your writing here, feel free to include subsections to structure your report if needed
% Please remove the note below in your submission
\note{Explain how you protocol from Section 1 is extended with fault-tolerance.}

\section{Fault-Tolerant Implementation}

% Start your writing here, feel free to include subsections to structure your report if needed
% Please remove the note below in your submission
\note{Explain how your fault-tolerant solution is implemented on both host and (especially) switch side. What challenges did you face and how did you solve them? A good place to start is the questions and hints from the Lab 5 document.}


\subsection{How to Run It}

% Start your writing here. Please remove the note below in your submission
\note{If you made any changes on how the workers start, control plane usage, etc, please include them here; otherwise remove this section.}

\section{Bonus: X}

% Start your writing here, feel free to include subsections to structure your report if needed
% Please remove the note below in your submission
\note{Include a section for each of the bonuses you attempt, if any; otherwise remove this section.}


\section{References}

% Start your writing here, please remove the note below in your submission
\note{Include your references if any; otherwise remove this section.}


\end{document}
